PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

## Sex

@@

# Neurological frequencies
** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
```{r neurological frequencies alsfrs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("alsfrs"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

>>>>

## Sex
```{r sex according to probable Covid}
sex_category_per_Covid_prop_total <- dat.raw %>%
  filter(!is.na(Sex)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  count(Sex, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(sex_category_per_Covid_prop_total)
sex_category_per_Covid_prop_total
```

## Smoking not available

## BMI not available

```{r}
key_worker_category_per_Covid_prop_total <- dat.raw %>%
  filter(!is.na(key_worker)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  count(key_worker, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(key_worker_category_per_Covid_prop_total)
key_worker_category_per_Covid_prop_total
```

@@

# Neurological frequencies
** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
```{r neurological frequencies alsfrs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("alsfrs"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```
